Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-03 WSSSPE3/report/WSSSPE3_review.tex
Section 2: More natural spacing without quotes.
editing changes from last 2 weeks - just starting
slight update to abstrcact

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). 
The report includes a description of the keynote presentation and a set of lightning
talks. It also focuses on the discussions, future steps, and future organization for
a set of self-organized working groups.
For each group, we include a point of contact and a landing
page that can be used by those who want to join that group's future activities.
The main challenge left by the workshop is to see if the groups will execute 
these activities that they have scheduled, and how the WSSSPE community
can encourage its members to follow suit.
\end{abstract}

\maketitle
%\newpage

@@

The first call also discussed the potential action topics that came out of
WSSSPE2, and requested additional suggestions. The combination of existing and
new topics led to the following 18 potential topics that were advertised in the
subsequent calls for participation:

\begin{quote}
\begin{itemize}
\renewcommand{\labelenumi}{\textbf{\theenumi}.}
\setlength{\rightmargin}{1em}

@@

\end{itemize}
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynote \label{sec:keynote}}
%\note{Lead: S.-C. Choi.  See \href{http://tinyurl.com/qbbqgsj}{slides} \& \href{http://tinyurl.com/q45kfcn}{video}.}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Turk talked about possible reasons why we want to sustain scientific software:
devotion to science and interests in pursuing the next stage of research; fun
and creative thrill in writing codes and papers; usefulness with measurable
impacts, for example, LINPACK and HDF groups providing data storage to
satellites, which goes beyond usefulness to necessity. Lastly, Turk presented
his wish list of questions to be answered in the future:
%
\begin{itemize}

>>>>

\begin{abstract}
This technical report records and discusses the Third Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE3). 
The report includes a description of the keynote presentation and a set of lightning
talks. It also focuses on the discussions, future steps, and future organization for
a set of self-organized working groups.
For each group, we include a point of contact and a landing
page that can be used by those who want to join that group's future activities.
The main challenge left by the workshop is to see if the groups will execute 
these activities that they have scheduled, and how the WSSSPE community
can encourage this to happen.
\end{abstract}

\maketitle
\newpage

@@

The first call also discussed the potential action topics that came out of
WSSSPE2, and requested additional suggestions. The combination of existing and
new topics led to the following 18 potential topics that were advertised in the
subsequent calls for participation:
%
%\begin{quote}
\begin{itemize}
\renewcommand{\labelenumi}{\textbf{\theenumi}.}
\setlength{\rightmargin}{1em}

@@

\end{itemize}
%\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynote}\label{sec:keynote}
%\note{Lead: S.-C. Choi.  See \href{http://tinyurl.com/qbbqgsj}{slides} \& \href{http://tinyurl.com/q45kfcn}{video}.}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Turk talked about possible reasons why we want to sustain scientific software:
devotion to science and interests in pursuing the next stage of research; fun
and creative thrill in writing codes and papers; usefulness with measurable
impacts, for example, LINPACK and HDF groups providing data storage to
satellites, which goes beyond usefulness to necessity. Lastly, Turk presented
his wishlist of questions to be answered in the future:
%
\begin{itemize}
